### 2022-05-17 paper/letter/letter.Rmd
Added to reply letter.

---
author: Prof. Dr. Pedro Rafael D. Marinho
return-address: 
  - Department of Statistics
  - Federal University of Paraíba
  - João Pessoa, Paraíba - PB, Brazil
return-email: pedro.rafael.marinho@gmail.com
papersize: letter
yourmail: pedro.rafael.marinho@gmail.com
return-url: https://prdm0.rbind.io/
urlcolor: blue
linkcolor: red
address:
  - "**Editor-in-Chief: Enrico Colosimo**"
  - "**Brazilian Journal of Probability and Statistics - BJPS**"
  - ""
subject: "A new family of distributions: properties and applications"
opening: | 
  | Dear **BJPS** Editor,
closing: Kind regards,
signature: |
  | Prof. Dr. Pedro Rafael D. Marinho
  | (DSc in Statistics from Federal University of Pernambuco)
output: 
  komaletter::komaletter:
    keep_tex: true
---

we would like to present the paper entitled **A new family of distributions: properties and applications** to the BJPS. This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two extra shape parameters and can be a better model than other existing classes of distributions. Simulations
are performed to verify the consistency of the estimators. Its flexibility is shown using two real data sets.

>>>>

---
author: Prof. Dr. Pedro Rafael D. Marinho
return-address: 
  - Department of Statistics
  - Federal University of Paraíba
  - João Pessoa, Paraíba - PB, Brazil
return-email: pedro.rafael.marinho@gmail.com
papersize: letter
yourmail: pedro.rafael.marinho@gmail.com
return-url: https://prdm0.rbind.io/
urlcolor: blue
linkcolor: red
address:
  - "**Executive Editor**"
  - "**REVSTAT**"
  - ""
subject: "A new family of distributions: properties and applications"
opening: | 
  | Dear **REVSTAT** Executive Editor,
closing: Kind regards,
signature: |
  | Prof. Dr. Pedro Rafael D. Marinho
  | (DSc in Statistics from Federal University of Pernambuco)
output: 
  komaletter::komaletter:
    keep_tex: true
---

we would like to present the paper entitled **A new family of distributions: properties and applications** to the REVSTAT. This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two extra shape parameters and can be a better model than other existing classes of distributions. Simulations
are performed to verify the consistency of the estimators. Its flexibility is shown using two real data sets.

### 2022-05-17 paper/letter/letter.tex
Added to reply letter.

\begin{letter}{\textbf{Editor-in-Chief: Enrico
Colosimo}\\\textbf{Brazilian Journal of Probability and Statistics -
BJPS}\\}
\opening{Dear \textbf{BJPS} Editor,}

we would like to present the paper entitled \textbf{A new family of
distributions: properties and applications} to the BJPS. This article
introduces a new family by combining the Marshall and Olkin-G and
Gamma-G classes. The family has only two extra shape parameters and can
be a better model than other existing classes of distributions.
Simulations are performed to verify the consistency of the estimators.
Its flexibility is shown using two real data sets.

>>>>

\begin{letter}{\textbf{Executive Editor}\\\textbf{REVSTAT}\\}
\opening{Dear \textbf{REVSTAT} Executive Editor,}

we would like to present the paper entitled \textbf{A new family of
distributions: properties and applications} to the REVSTAT. This article
introduces a new family by combining the Marshall and Olkin-G and
Gamma-G classes. The family has only two extra shape parameters and can
be a better model than other existing classes of distributions.
Simulations are performed to verify the consistency of the estimators.
Its flexibility is shown using two real data sets.
